%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

    \cventry
    {Developer} % Job title
    {SmartGarden - Freelancer} % Organization
    {Ha Noi} % Location
    {05/2018 - 02/2019} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Overview: Automatic system that controls moisture, temperature, water pumping for garden. }
            \item {Develop Android app: written in Kotlin. }
            \item {Develop Website: written in AngularJS. }
            \item {Develop Sensor Node: written in C++ with ESP8266 module. }
            \item {Design realtime remote-control flow from Android application or Web app over Websocket and MQTT.}
            \item {Use Firebase authentication, Firebase database, Firebase Hosting.}
        \end{cvitems}
    }

    \cventry
    {Developer, Tester} % Job title
    {SMS System - IRIS Media Company} % Organization
    {Ha Noi} % Location
    {06/2019 - 08/2020} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Overview: Use GSM devices to send and receive SMS to customer handsets}
            \item {Develop GSM client software: Python with PySimpleGUI, interactive with GSM devices, receive command from backend server, send SMS and report results.}
            \item {Develop Backend server: Spring Boot Framework with RESTful APIs and RabbitMQ}
            \item {Optimize and enhance performance up to 50.000 sms sent daily. }
            \item {Support customers in integrating APIs.}
        \end{cvitems}
    }

    \cventry
    {Developer} % Job title
    {Delivery Service - Advesa Digital Solutions} % Organization
    {Ha Noi} % Location
    {09/2020 - now} % Date(s)
    {
        \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Work in Cantec Delivery, Cantec Express that are proprietary projects owned by Advesa that provide same-day delivery service.}
            \item {Develop Backend server: Python, Django REST Framework.}
            \item {Implement business logic: payment record, commission rate...}
            \item {Debug and implement multiple timezones problems.}
            \item {Create partner API for 3rd parties integration.}
            \item {Participate in designing system architect and services communication.}
            \item {Design database structure and optimize MongoDB queries.}
            \item {Deploy, debug, monitor, scale, maintain systems on GCE and GKE.}
            \item {Support Frontend, Mobile and 3rd parties teams to consume RESTful APIs.}
            \item {Enhance system performance with Celery asynchronous task queue.}
            \item {Refactor and enhance codebase quality.}
        \end{cvitems}
    }

\end{cventries}
